---
title: "Second BM25 A/B test (ja, zh, th) Analysis"
subtitle: "Draft"
author:
- <a href = 'https://meta.wikimedia.org/wiki/User:EBernhardson_(WMF)'>Erik Bernhardson</a> (Engineering)
- <a href = 'https://www.mediawiki.org/wiki/User:DCausse_(WMF)'>David Causse</a> (Engineering & Report)
- <a href = 'https://meta.wikimedia.org/wiki/User:TJones_(WMF)'>Trey Jones</a> (Engineering & Review)
- <a href = 'https://meta.wikimedia.org/wiki/User:MPopov_(WMF)'>Mikhail Popov</a> (Review)
- <a href = 'https://meta.wikimedia.org/wiki/User:DTankersley_(WMF)'>Deb Tankersley</a> (Product Management)
- <a href = 'https://meta.wikimedia.org/wiki/User:CXie_(WMF)'>Chelsy Xie</a> (Analysis & Report)
date: "`r as.character(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    css: style.css
    fig_caption: yes
    fig_width: 10
    fig_height: 6
    highlight: zenburn
    keep_md: yes
    mathjax: https://tools-static.wmflabs.org/cdnjs/ajax/libs/mathjax/2.6.1/MathJax.js?config=TeX-AMS-MML_HTMLorMML
    md_extensions: +raw_html +markdown_in_html_blocks +tex_math_dollars +fancy_lists +startnum +lists_without_preceding_blankline
    self_contained: no
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
---
<script language="JavaScript">
$(function() {
  /* Lets the user click on the images to view them in full resolution. */
  $("div.figure img").wrap(function() {
    var link = $('<a/>');
    link.attr('href', $(this).attr('src'));
    link.attr('title', $(this).attr('alt'));
    link.attr('target', '_blank');
    return link;
  });
});
</script>
<p>{ <a href="https://github.com/wikimedia-research/Discovery-Search-2ndTest-BM25_jazhth/blob/master/docs/index.Rmd">RMarkdown Source</a> | <a href="https://github.com/wikimedia-research/Discovery-Search-2ndTest-BM25_jazhth">Analysis Codebase</a> }</p>
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
options(digits = 3, scipen = 500)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
path <- function(x) {
  if (grepl("docs", getwd(), fixed = TRUE)) {
    return(file.path("..", x))
  } else {
    return(x)
  }
}
# Font to go together with HTML version of report: http://www.latofonts.com/
# extrafont::font_import("~/Downloads/Lato2OFL")
```
```{r captions, echo = FALSE}
# Manual figure & table captioning:
library(magrittr)
library(captioner) # install.packages("captioner")
table_caps <- captioner(prefix = "Table")
figure_caps <- captioner(prefix = "Figure")
code_caps <- captioner(prefix = "Snippet")
# Custom caption formatting and printing:
format_caption <- function(caps, name) {
  return({
    sub(caps(name, display = "cite"),
      paste0("**", caps(name, display = "cite"),"**"),
      caps(name, display = "full"), fixed = TRUE) %>%
    sub("  ", " ", ., fixed = TRUE)
  })
}
print_caption <- function(formatted_caption) {
  cat(paste0('<p class = "caption">', formatted_caption, '</p>', collapse = ''))
}
# Add captions:
#code_caps(name = "bm25_query", caption = "Query used to extract BM25 test data from our event logging database.", display = FALSE)
#table_caps(name = "clustering_example", caption = "Example of how choice of linkage affects clustering of queries from a real search session.", display = FALSE)
table_caps(name = "group_counts", caption = "Counts of sessions anonymously tracked and events collected during the second A/B test (Oct 27 - Nov 15).", display = FALSE)
table_caps(name = "group_counts2", caption = "After searchResultPage De-duplication, Counts of sessions anonymously tracked and events collected during the second A/B test (Oct 27 - Nov 15).", display = FALSE)
#figure_caps("query_reform_counts", "Proportions of searches with 0, 1, 2, and 3+ query reformulations.", display = FALSE)
#figure_caps("query_reform_prop", "Proportions of searches where user reformulated their query.", display = FALSE)
figure_caps("zrr", "Zero results rate is the proportion of searches in which the user received zero results.", display = FALSE)
figure_caps("paulscore", "Average per-group PaulScore for various values of F (0.1, 0.5, and 0.9) with bootstrapped confidence intervals.", display = FALSE)
figure_caps("engagement_overall", "Clickthrough rates of test groups.", display = FALSE)
#figure_caps("engagement", "Clickthrough rates of test groups after splitting searches into those having query reformulations and those without query reformulations.", display = FALSE)
figure_caps("first_clicked", "First clicked result's position by group.", display = FALSE)
```

```{r install_packages, eval = FALSE}
# Install packages used in the report:
install.packages(c("devtools", "tidyverse", "binom"))
devtools::install_github("hadley/ggplot2")
# ^ development version of ggplot2 includes subtitles
devtools::install_github("wikimedia/wikimedia-discovery-polloi")
# ^ for converting 100000 into 100K via polloi::compress()
```
```{r load_packages}
# Load packages that we will be using in this report:
library(tidyverse) # for ggplot2, dplyr, tidyr, broom, etc.
library(binom) # for Bayesian confidence intervals of proportions
```

```{r paulscore_functions, cache = TRUE}
# PaulScore Calculation
query_score <- function(positions, F) {
   if (length(positions) == 1 || all(is.na(positions))) {
    # no clicks were made
    return(0)
   } else {
     positions <- positions[!is.na(positions)] # when operating on 'events' dataset, searchResultPage events won't have positions
  return(sum(F^positions))
   }
}
# Bootstrapping
bootstrap_mean <- function(x, m, seed = NULL) {
  if (!is.null(seed)) {
    set.seed(seed)
  }
  n <- length(x)
  return(replicate(m, mean(x[sample.int(n, n, replace = TRUE)])))
}
```

## Results

### Data

```{r data, cache = TRUE}
# Import events fetched from MySQL
load(path("data/ab-test_bm25.RData"))
events <- events[!duplicated(events$event_id),]
events <- events %>%
  group_by(date, wiki, test_group, session_id, search_id) %>%
  filter("searchResultPage" %in% action) %>%
  ungroup %>% as.data.frame() # remove search_id without SERP asscociated
events$test_group <- factor(
  events$test_group,
  levels = c("bm25:control", "bm25:inclinks_pv"),
  labels = c("Control Group (tf–idf)", "Using per-field query builder with incoming links and pageviews as QIFs"))
cirrus <- readr::read_tsv(path("data/ab-test_bm25_cirrus-results.tsv.gz"), col_types = "cccc")
cirrus <- cirrus[!duplicated(cirrus),]
events <- left_join(events, cirrus, by = c("event_id", "page_id", "cirrus_id"))
rm(cirrus)
```
The test was deployed on October 27th and ran for a week (thwiki ran longer, till Nov 15.), collecting a total of `r polloi::compress(nrow(events), 1)` events from `r polloi::compress(length(unique(events$search_id)), 1)` unique sessions. See `r table_caps("group_counts", display = "cite")` for counts broken down by wiki and test group.

```{r summary, results = "asis", dependson = "data"}
events_summary <- events %>%
  group_by(wiki, `Test group` = test_group) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Events recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Events recorded` = sum(.$`Events recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Events recorded` = prettyNum(`Events recorded`, big.mark = ","))
knitr::kable(events_summary, format = "markdown", align = c("l", "l", "r", "r"))
```
```{r summary_caption, results = "asis", echo = FALSE}
print_caption(format_caption(table_caps, "group_counts"))
```

An issue we noticed with the event logging is that when the user goes to the next page of search results or clicks the Back button after visiting a search result, a new page ID is generated for the search results page. The page ID is how we connect click events to search result page events. There is currently a Phabricator ticket ([T146337](https://phabricator.wikimedia.org/T146337)) for addressing these issues. For this analysis, we de-duplicated by connecting search engine results page (searchResultPage) events that have the exact same search query, and then connected click events together based on the searchResultPage connectivity.

```{r searchResultPage_deduplication, dependson = "data", cache = TRUE}
temp <- events %>%
  filter(action == "searchResultPage") %>%
  group_by(session_id, search_id, query) %>%
  mutate(new_page_id = min(page_id)) %>%
  ungroup %>%
  select(c(page_id, new_page_id)) %>%
  distinct
events <- left_join(events, temp, by = "page_id"); rm(temp)
events$new_page_id[is.na(events$new_page_id)] <- events$page_id[is.na(events$new_page_id)] 
temp <- events %>%
  filter(action == "searchResultPage") %>%
  arrange(new_page_id, ts) %>%
  mutate(dupe = duplicated(new_page_id, fromLast = FALSE)) %>%
  select(c(event_id, dupe))
events <- left_join(events, temp, by = "event_id"); rm(temp)
events$dupe[events$action != "searchResultPage"] <- FALSE
events <- events[!events$dupe & !is.na(events$new_page_id), ] %>%
  select(-c(page_id, dupe)) %>%
  rename(page_id = new_page_id) %>%
  arrange(date, session_id, search_id, page_id, desc(action), ts)
```
```{r aggregation, dependson = c("searchResultPage_deduplication", "paulscore_functions"), cache = TRUE}
# Summarize on a page-by-page basis for each SERP:
searches <- events %>%
  group_by(wiki, `test group` = test_group, session_id, search_id, page_id) %>%
  filter("searchResultPage" %in% action) %>% # filter out searches where we have clicks but not searchResultPage events
  summarize(ts = ts[1], query = query[1],
            results = ifelse(n_results_returned[1] > 0, "some", "zero"),
            clickthrough = "click" %in% action,
            `no. results clicked` = length(unique(position_clicked))-1,
            `first clicked result's position` = ifelse(clickthrough, position_clicked[2], NA),
            `result page IDs` = paste(unique(result_pids[!is.na(result_pids)]), collapse=','),
            `Query score (F=0.1)` = query_score(position_clicked, 0.1),
            `Query score (F=0.5)` = query_score(position_clicked, 0.5),
            `Query score (F=0.9)` = query_score(position_clicked, 0.9)) %>%
  arrange(ts)
searches$`result page IDs`[searches$`result page IDs`==""] <- NA
```
After de-duplicating, we collapsed `r polloi::compress(nrow(events), 1)` (searchResultPage and click) events into `r polloi::compress(nrow(searches), 1)` searches. See `r table_caps("group_counts2", display = "cite")` for counts broken down by wiki and test group.

```{r summary2, results = "asis", dependson = c("searchResultPage_deduplication","aggregation")}
events_summary2 <- events %>%
  group_by(wiki, `Test group` = test_group) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Events recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Events recorded` = sum(.$`Events recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Events recorded` = prettyNum(`Events recorded`, big.mark = ","))
searches_summary <- searches %>%
  group_by(wiki, `Test group` = `test group`) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Searches recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Searches recorded` = sum(.$`Searches recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Searches recorded` = prettyNum(`Searches recorded`, big.mark = ","))
knitr::kable(inner_join(searches_summary, events_summary2, by=c("wiki", "Test group", "Search sessions")), 
             format = "markdown", align = c("l", "l", "r", "r", "r"))
```
```{r summary_caption2, results = "asis", echo = FALSE}
print_caption(format_caption(table_caps, "group_counts2"))
```

There are `r polloi::compress(length(unique(events$page_id[events$action=="visitPage"])), 1)` visitPage events. See the table below for counts broken down by wiki and test group.

```{r aggregation_visits, dependson = "searchResultPage_deduplication", cache = TRUE}
# Summarize on a page-by-page basis for each visitPage:
clickedResults <- events %>%
  group_by(wiki, `test group` = test_group, session_id, search_id, page_id) %>%
  filter("visitPage" %in% action) %>% #only checkin and visitPage action
  summarize(ts = ts[1], 
            dwell_time=ifelse("checkin"%in% action, max(checkin, na.rm=T), 0),
            scroll=sum(scroll)>0) %>%
  arrange(ts)
clickedResults$dwell_time[is.na(clickedResults$dwell_time)] <- 0
```
```{r summary3, results = "asis", dependson = "aggregation_visits"}
clickedResults_summary <- clickedResults %>%
  group_by(wiki, `Test group` = `test group`) %>%
  summarize(`Visited pages` = length(unique(page_id))) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Visited pages` = sum(.$`Visited pages`)
    ))
  } %>%
  mutate(`Visited pages` = prettyNum(`Visited pages`, big.mark = ","))
knitr::kable(clickedResults_summary, format = "markdown", align = c("l", "l", "r", "r"))
```

### Zero Results Rate

In `r figure_caps("zrr", display = "cite")`, we see that the test group had a significantly lower ZRR.

```{r zrr, dependson = "query_clustering", cache = TRUE}
zrr_pages <- searches %>%
  group_by(`test group`, results) %>%
  tally %>%
  spread(results, n) %>%
  mutate(`zero results rate` = zero/(some + zero)) %>%
  ungroup
zrr_pages <- cbind(zrr_pages, as.data.frame(binom:::binom.bayes(zrr_pages$zero, n = zrr_pages$some + zrr_pages$zero)[, c("mean", "lower", "upper")]))
```
```{r zrr_caption, echo = FALSE}
zrr_cap <- format_caption(figure_caps, "zrr")
```
```{r zrr_eda, fig.cap = zrr_cap, dependson = "zrr"}
zrr_pages %>%
  ggplot(aes(x = `test group`, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(limits = rev(levels(events$test_group))) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_color_brewer("Test Group", palette = "Set1", guide = FALSE) +
  labs(x = NULL, y = "Zero Results Rate",
       title = "Proportion of searches that did not yield any results, by test group",
       subtitle = "With 95% credible intervals.") +
  geom_text(aes(label = sprintf("%.2f%%", 100 * `zero results rate`),
                vjust = "bottom", hjust = "center"), nudge_x = 0.1) #+
  #theme_minimal(base_family = "Lato")
```
```{r zrr_eda2}
zrr_pages <- searches %>%
  group_by(wiki, `test group`, results) %>%
  tally %>%
  spread(results, n) %>%
  mutate(`zero results rate` = zero/(some + zero)) %>%
  ungroup
zrr_pages <- cbind(zrr_pages, as.data.frame(binom:::binom.bayes(zrr_pages$zero, n = zrr_pages$some + zrr_pages$zero)[, c("mean", "lower", "upper")]))
zrr_pages %>%
  ggplot(aes(x = `test group`, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(limits = rev(levels(events$test_group))) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_color_brewer("Test Group", palette = "Set1", guide = FALSE) +
  labs(x = NULL, y = "Zero Results Rate",
       title = "Proportion of searches that did not yield any results, by test group and wiki",
       subtitle = "With 95% credible intervals.") +
  geom_text(aes(label = sprintf("%.2f%%", 100 * `zero results rate`),
                vjust = "bottom", hjust = "center"), nudge_x = 0.1) +
  facet_wrap(~ wiki, ncol = 3) 
```

### PaulScore

In `r figure_caps("paulscore", display = "cite")`, we see that the test group had slightly lower PaulScores.

```{r paulscores, dependson = "query_clustering", cache = TRUE}
set.seed(777)
paulscores <- searches %>%
  ungroup %>%
  filter(clickthrough==TRUE) %>% #???
  select(c(`test group`, `Query score (F=0.1)`, `Query score (F=0.5)`, `Query score (F=0.9)`)) %>%
  gather(`F value`, `Query score`, -`test group`) %>%
  mutate(`F value` = sub("^Query score \\(F=(0\\.[159])\\)$", "F = \\1", `F value`)) %>%
  group_by(`test group`, `F value`) %>%
  summarize(
    PaulScore = mean(`Query score`),
    Interval = paste0(quantile(bootstrap_mean(`Query score`, 1000), c(0.025, 0.975)), collapse = ",")
  ) %>%
  extract(Interval, into = c("Lower", "Upper"), regex = "(.*),(.*)", convert = TRUE)
```

```{r paulscores_caption, echo = FALSE}
paulscore_cap <- format_caption(figure_caps, "paulscore")
```
```{r paulscores_eda, fig.cap = paulscore_cap, dependson = "paulscores"}
paulscores %>%
  ggplot(aes(x = `F value`, y = PaulScore, color = `test group`)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), position = position_dodge(width = 0.7)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  #scale_y_continuous(limits = c(0.2, 0.35)) +
  labs(x = NULL, y = "PaulScore(F)",
       title = "PaulScore(F) by test group and value of F",
       subtitle = "With bootstrapped 95% confidence intervals.") +
  geom_text(aes(label = sprintf("%.3f", PaulScore), y = Upper + 0.01, vjust = "bottom"),
            position = position_dodge(width = 0.7)) +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom") 
```
```{r paulscores_eda2}
set.seed(777)
paulscores <- searches %>%
  ungroup %>%
  filter(clickthrough==TRUE) %>% 
  select(c(wiki, `test group`, `Query score (F=0.1)`, `Query score (F=0.5)`, `Query score (F=0.9)`)) %>%
  gather(`F value`, `Query score`, -c(`test group`, wiki)) %>%
  mutate(`F value` = sub("^Query score \\(F=(0\\.[159])\\)$", "F = \\1", `F value`)) %>%
  group_by(wiki, `test group`, `F value`) %>%
  summarize(
    PaulScore = mean(`Query score`),
    Interval = paste0(quantile(bootstrap_mean(`Query score`, 1000), c(0.025, 0.975)), collapse = ",")
  ) %>%
  extract(Interval, into = c("Lower", "Upper"), regex = "(.*),(.*)", convert = TRUE)
paulscores %>%
  ggplot(aes(x = `F value`, y = PaulScore, color = `test group`)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), position = position_dodge(width = 0.7)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  #scale_y_continuous(limits = c(0.2, 0.35)) +
  labs(x = NULL, y = "PaulScore(F)",
       title = "PaulScore(F) by wiki, test group and value of F",
       subtitle = "With bootstrapped 95% confidence intervals.") +
  geom_text(aes(label = sprintf("%.3f", PaulScore), y = Upper + 0.01, vjust = "bottom"),
            position = position_dodge(width = 0.7)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom") 
```

### Engagement

In Figures `r figure_caps("engagement_overall", display = "num")`, we see that the test group had a significantly lower Clickthrough rate.

```{r engagement_overall, dependson = "query_reformulations", cache = TRUE}
engagement_overall <- searches %>%
  filter(results=="some") %>% #???
  group_by(`test group`) %>%
  summarize(clickthroughs = sum(clickthrough > 0),
            searches = n(), ctr = clickthroughs/searches) %>%
  ungroup
engagement_overall <- cbind(
  engagement_overall,
  as.data.frame(
    binom:::binom.bayes(
      engagement_overall$clickthroughs,
      n = engagement_overall$searches)[, c("mean", "lower", "upper")]
  )
)
```
```{r engagement_overall_caption, echo = FALSE}
engagement_overall_cap <- format_caption(figure_caps, "engagement_overall")
```
```{r engagement_overall_eda, fig.cap = engagement_overall_cap, dependson = "engagement_overall"}
engagement_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Clickthrough rate",
       title = "Engagement with search results by test group") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * ctr), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom")
```
```{r engagement_overall_eda2}
engagement_overall <- searches %>%
  filter(results=="some") %>% 
  group_by(wiki, `test group`) %>%
  summarize(clickthroughs = sum(clickthrough > 0),
            searches = n(), ctr = clickthroughs/searches) %>%
  ungroup
engagement_overall <- cbind(
  engagement_overall,
  as.data.frame(
    binom:::binom.bayes(
      engagement_overall$clickthroughs,
      n = engagement_overall$searches)[, c("mean", "lower", "upper")]
  )
)
engagement_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Clickthrough rate",
       title = "Engagement with search results by test group and wiki") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * ctr), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom")
```

### First Clicked Result's Position

In `r figure_caps("first_clicked", display = "cite")`, we see that test group users were less likely to click on the first search result first than the control group.

```{r first_clicked_position, dependson = "query_reformulations", cache = TRUE}
safe_ordinals <- function(x) {
  return(vapply(x, toOrdinal::toOrdinal, ""))
}
first_clicked <- searches %>%
  filter(results == "some" & clickthrough & !is.na(`first clicked result's position`)) %>%
  mutate(`first clicked result's position` = ifelse(`first clicked result's position` < 4, safe_ordinals(`first clicked result's position` + 1), "5th or higher")) %>%
  group_by(`test group`, `first clicked result's position`) %>%
  tally %>%
  mutate(total = sum(n), prop = n/total) %>%
  ungroup
set.seed(0)
temp <- as.data.frame(binom:::binom.bayes(first_clicked$n, n = first_clicked$total, tol = .Machine$double.eps^0.1)[, c("mean", "lower", "upper")])
first_clicked <- cbind(first_clicked, temp); rm(temp)
```
```{r first_clicked_position_caption, echo = FALSE}
first_clicked_cap <- format_caption(figure_caps, "first_clicked")
```
```{r first_clicked_position_eda, fig.cap = first_clicked_cap, dependson = "first_clicked_position"}
first_clicked %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  geom_text(aes(label = sprintf("%.1f", 100 * prop), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0.005), breaks = seq(0, 1, 0.01)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  facet_wrap(~ `first clicked result's position`, scale = "free_y", nrow = 1) +
  labs(x = NULL, y = "Proportion of searches",
       title = "Position of the first clicked result",
       subtitle = "With 95% credible intervals") +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "gray90"),
        panel.border = element_rect(color = "gray30", fill = NA))
```
```{r first_clicked_position_eda2, fig.height=10 }
first_clicked <- searches %>%
  filter(results == "some" & clickthrough & !is.na(`first clicked result's position`)) %>%
  mutate(`first clicked result's position` = ifelse(`first clicked result's position` < 4, safe_ordinals(`first clicked result's position` + 1), "5th or higher")) %>%
  group_by(wiki, `test group`, `first clicked result's position`) %>%
  tally %>%
  mutate(total = sum(n), prop = n/total) %>%
  ungroup
set.seed(0)
temp <- as.data.frame(binom:::binom.bayes(first_clicked$n, n = first_clicked$total, tol = .Machine$double.eps^0.1)[, c("mean", "lower", "upper")])
first_clicked <- cbind(first_clicked, temp); rm(temp)
first_clicked %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  geom_text(aes(label = sprintf("%.1f", 100 * prop), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0.005), breaks = seq(0, 1, 0.01)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  facet_wrap(~ wiki+`first clicked result's position`, scale = "free_y", ncol=5, nrow = 3) +
  labs(x = NULL, y = "Proportion of searches",
       title = "Position of the first clicked result",
       subtitle = "With 95% credible intervals") +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "gray90"),
        panel.border = element_rect(color = "gray30", fill = NA))
```

### Dwell Time per visit page

The figures below show the survival curve for each test group and wikis. Except zhwiki, users are more likely to stay longer on visit pages.

```{r dwell_time_eda}
clickedResults %>%
  split(.$`test group`) %>% 
  map_df(function(df) {
    seconds <- c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420)
    seshs <- as.data.frame(do.call(cbind, lapply(seconds, function(second) {
      return(sum(df$dwell_time >= second))
    })))
    names(seshs) <- seconds
    return(cbind(`test group` = head(df$`test group`, 1), n = seshs$`0`, seshs, `450`=seshs$`420`))
  }) %>%
  gather(seconds, visits, -c(`test group`, n)) %>%
  mutate(seconds = as.numeric(seconds)) %>%
  group_by(`test group`, seconds) %>%
  mutate(proportion = visits/n) %>%
  ungroup() %>%
  ggplot(aes(group=`test group`, color=`test group`)) +
  geom_step(aes(x = seconds, y = proportion), direction = "hv") +
  scale_x_continuous(name = "T (Dwell Time)", breaks=c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420))+ 
  scale_y_continuous("Proportion of visits longer than T", labels = scales::percent_format(),
                     breaks = seq(0, 1, 0.1)) +
  theme(legend.position = "bottom")
```

```{r dwell_time_eda_wiki}
clickedResults %>%
  split(list(.$wiki, .$`test group`)) %>% 
  map_df(function(df) {
    seconds <- c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420)
    seshs <- as.data.frame(do.call(cbind, lapply(seconds, function(second) {
      return(sum(df$dwell_time >= second))
    })))
    names(seshs) <- seconds
    return(cbind(wiki=head(df$wiki, 1), `test group` = head(df$`test group`, 1), n = seshs$`0`, seshs, `450`=seshs$`420`))
  }) %>%
  gather(seconds, visits, -c(wiki, `test group`, n)) %>%
  mutate(seconds = as.numeric(seconds)) %>%
  group_by(wiki, `test group`, seconds) %>%
  mutate(proportion = visits/n) %>%
  ungroup() %>%
  ggplot(aes(group=`test group`, color=`test group`)) +
  geom_step(aes(x = seconds, y = proportion), direction = "hv") +
  scale_x_continuous(name = "T (Dwell Time)", breaks=c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420))+ 
  scale_y_continuous("Proportion of visits longer than T", labels = scales::percent_format(),
                     breaks = seq(0, 1, 0.1)) +
  theme(legend.position = "bottom") +
  facet_wrap(~ wiki, ncol=1, nrow =3)
```

### Proportion of visit pages with scroll

Users in the test group are more likely to scroll on the visit page, but the differences are not statistically significant.

```{r scroll_eda}
scroll_overall <- clickedResults %>%
  group_by(`test group`) %>%
  summarize(scrolls=sum(scroll), visits=n(), proportion = sum(scroll)/n()) %>%
  ungroup
scroll_overall <- cbind(
  scroll_overall,
  as.data.frame(
    binom:::binom.bayes(
      scroll_overall$scrolls,
      n = scroll_overall$visits)[, c("mean", "lower", "upper")]
  )
)
scroll_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Proportion of visits",
       title = "Proportion of visits with scroll by test group") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  theme(legend.position = "bottom")
```

```{r scroll_eda_wiki}
scroll_overall <- clickedResults %>%
  group_by(wiki, `test group`) %>%
  summarize(scrolls=sum(scroll), visits=n(), proportion = sum(scroll)/n()) %>%
  ungroup
scroll_overall <- cbind(
  scroll_overall,
  as.data.frame(
    binom:::binom.bayes(
      scroll_overall$scrolls,
      n = scroll_overall$visits)[, c("mean", "lower", "upper")]
  )
)
scroll_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Proportion of visits",
       title = "Proportion of visits with scroll by test group and wiki") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom")
```

### Query Reformulation

First, we tokenized queries from zhwiki, jawiki and thwiki with [jieba](https://github.com/fxsjy/jieba), [tinysegmenter](https://pypi.python.org/pypi/tinysegmenter) and [elasticsearch termvectors api](https://www.elastic.co/guide/en/elasticsearch/reference/current/docs-termvectors.html) separately. Then we filter out [stop words](https://github.com/6/stopwords-json).

```{r tokenization}
# See tokenize.R for more details
library(jiebaR)
library(ropencc)

#thwiki
load("../data/tokens_th.RData")
tokens_th <- output; rm(output)
stopword_th <- jsonlite::fromJSON("../resource/th.json")
tokens_th <- filter_segment(tokens_th,stopword_th)

#zhwiki
queries_zh <- searches[searches$wiki=="zhwiki", c("page_id","query")]
queries_zh$query <- gsub("[[:punct:]]", " ", queries_zh$query)
stopword_zh <- jsonlite::fromJSON("../resource/zh.json")
ccst = converter(S2T)
stopword_zh <- union(ccst[stopword_zh], stopword_zh)
mixseg = worker(bylines = TRUE)
tokens_zh <- mixseg[queries_zh$query]
tokens_zh <- filter_segment(tokens_zh,stopword_zh)
names(tokens_zh) <- queries_zh$page_id

#jawiki
tokens_ja <- jsonlite::fromJSON("../data/tokens_ja.json")
stopword_ja <- jsonlite::fromJSON("../resource/ja.json")
tokens_ja <- filter_segment(tokens_ja,stopword_ja)
tokens_ja <- lapply(tokens_ja, function(x) gsub(" +","",x)) # strip space before/after string
```

We consider two queries as a reformulation if 1) they are from the same search session and share at least one result, or 2) they are from the same search session and share at least one word.

```{r reformulation, dependson="tokenization", cache = TRUE}
library(igraph)
all_tokens <- c(tokens_ja, tokens_zh, tokens_th)

overlapping_results <- function(x) {
  if (all(is.na(x))) {
    return(diag(length(x)))
  }
  input <- strsplit(stringr::str_replace_all(x, "[\\[\\]]", ""), ",")
  output <- vapply(input, function(y) {
    temp <- vapply(input, function(z) { length(intersect(z, y)) }, 0L)
    temp[is.na(x)] <- 0L
    return(temp)
  }, rep(0L, length(input)))
  diag(output) <- 1L
  return(output)
}

reformulation <- function(result_pids, page_ids, all_tokens) {
  if(length(page_ids)==1){
    return(data.frame(n_search=1, n_reformulate="0"))
  }
  # result overlap
  overlaps_res <- overlapping_results(result_pids)
  # tokens overlap
  this_tokens <- all_tokens[page_ids]
  overlaps_token <- vapply(this_tokens, function(y) {
    temp <- vapply(this_tokens, function(z) { length(intersect(z, y)) }, 0L)
    temp[is.na(this_tokens)] <- 0L
    return(temp)
  }, rep(0L, length(this_tokens)))
  diag(overlaps_token) <- 1L
  
  overlaps_all <- (overlaps_res + overlaps_token) > 0
  diag(overlaps_all) <- 0L
  graph_object <- graph_from_adjacency_matrix(overlaps_all, mode = c("undirected"), diag = F)
  csize <- clusters(graph_object)$csize
  return(data.frame(n_search=length(csize), n_reformulate=ifelse(length(csize)>1,paste(csize-1, collapse=',' ), as.character(csize-1))))
}

reform_times <- searches %>% 
  group_by(wiki, `test group`, session_id, search_id) %>% 
  do(reformulation(.$`result page IDs`, .$page_id, all_tokens))
```

We grouped searches together using the rules above, then we have 51354 total search groups.

```{r reform_n_search_group}
reform_times %>% ungroup %>%
  mutate(n_search=ifelse(n_search>=10,"10+",n_search)) %>%
  group_by(n_search) %>%
  summarise(n_session=n()) %>%
  mutate(prop=n_session/sum(n_session)) %>%
  ggplot(aes(x = n_search, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous("Proportion of search sessions", labels = scales::percent_format()) +
  scale_x_discrete("Number of Search Groups", limits = c(1:9, "10+")) +
  geom_text(aes(label = sprintf("%.1f%%", 100*prop)), nudge_y = 0.025) +
  ggthemes::theme_tufte(base_family = "Gill Sans", base_size = 14) +
  ggtitle("Proportion of search sessions making N search groups")
```

We can see that test group users are less likely to reformulate their queries.

```{r reform_eda1}
reformulation_counts <- reform_times %>%
  group_by(`test group`) %>%
  summarize(`searches with query reformulations` = sum(as.numeric(unlist(lapply(n_reformulate, function(x) strsplit(x, ",")))) > 0),
            searches = sum(n_search),
            proportion = `searches with query reformulations`/searches) %>%
  ungroup
reformulation_counts <- cbind(
  reformulation_counts,
  as.data.frame(
    binom:::binom.bayes(
      reformulation_counts$`searches with query reformulations`,
      n = reformulation_counts$searches,
      tol = .Machine$double.eps^0.1)[, c("mean", "lower", "upper")]
  )
)
reformulation_counts %>%
  ggplot(aes(x = `test group`, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(limits = rev(levels(events$test_group))) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_color_brewer("Test Group", palette = "Set1", guide = FALSE) +
  labs(x = NULL, y = "% of searches with query reformulations",
       title = "Searches with reformulated queries by test group",
       subtitle = "Queries were grouped when they shared common results or common key words") +
  geom_text(aes(label = sprintf("%.2f%%", 100 * proportion),
                vjust = "bottom", hjust = "center"), nudge_x = 0.1)
```

```{r reform_eda1_wiki}
reformulation_counts <- reform_times %>%
  group_by(wiki, `test group`) %>%
  summarize(`searches with query reformulations` = sum(as.numeric(unlist(lapply(n_reformulate, function(x) strsplit(x, ",")))) > 0),
            searches = sum(n_search),
            proportion = `searches with query reformulations`/searches) %>%
  ungroup
reformulation_counts <- cbind(
  reformulation_counts,
  as.data.frame(
    binom:::binom.bayes(
      reformulation_counts$`searches with query reformulations`,
      n = reformulation_counts$searches)[, c("mean", "lower", "upper")]
  )
)
reformulation_counts %>%
  ggplot(aes(x = 1, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  labs(x = NULL, y = "% of searches with query reformulations",
       title = "Searches with reformulated queries by test group and wiki",
       subtitle = "Queries were grouped when they shared common results or common key words") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  theme(legend.position = "bottom")+
  facet_wrap(~ wiki, ncol = 3)
```

```{r reform_eda2}
count_reformulation <- function(n_reformulate){
  temp <- as.numeric(unlist(lapply(n_reformulate, function(x) strsplit(x, ","))))
  temp <- ifelse(temp>=3, "3+", temp)
  output <- as.data.frame(table(temp))
  output$proportion <- output$Freq/sum(output$Freq)
  colnames(output)[1] <- "query reformulations"
  return(output)
}
reform_times %>%
  group_by(`test group`) %>%
  do(count_reformulation(.$n_reformulate)) %>%
  ggplot(aes(x = `query reformulations`, y = proportion, fill = `test group`)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), vjust = "bottom"),
            position = position_dodge(width = 1)) +
  labs(y = "Proportion of searches", x = "Approximate number of query reformulations per grouped search",
       title = "Number of query reformulations by test group",
       subtitle = "Queries were grouped when they shared common results or common key words") +
  theme(legend.position = "bottom")
```

```{r reform_eda2_wiki}
reform_times %>%
  group_by(wiki, `test group`) %>%
  do(count_reformulation(.$n_reformulate)) %>%
  ggplot(aes(x = `query reformulations`, y = proportion, fill = `test group`)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), vjust = "bottom"),
            position = position_dodge(width = 1)) +
  labs(y = "Proportion of searches", x = "Approximate number of query reformulations per grouped search",
       title = "Number of query reformulations by test group and wiki",
       subtitle = "Queries were grouped when they shared common results or common key words") +
  theme(legend.position = "bottom")+
  facet_wrap(~ wiki, ncol = 3)
```