---
title: "Second BM25 A/B test (ja, zh, th) Analysis"
author:
- <a href = 'https://meta.wikimedia.org/wiki/User:EBernhardson_(WMF)'>Erik Bernhardson</a> (Engineering)
- <a href = 'https://www.mediawiki.org/wiki/User:DCausse_(WMF)'>David Causse</a> (Engineering & Report)
- <a href = 'https://meta.wikimedia.org/wiki/User:TJones_(WMF)'>Trey Jones</a> (Engineering & Review)
- <a href = 'https://meta.wikimedia.org/wiki/User:MPopov_(WMF)'>Mikhail Popov</a> (Review)
- <a href = 'https://meta.wikimedia.org/wiki/User:DTankersley_(WMF)'>Deb Tankersley</a> (Product Management)
- <a href = 'https://meta.wikimedia.org/wiki/User:CXie_(WMF)'>Chelsy Xie</a> (Analysis & Report)
date: "`r as.character(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    css: style.css
    fig_caption: yes
    fig_width: 10
    fig_height: 6
    highlight: zenburn
    keep_md: yes
    mathjax: https://tools-static.wmflabs.org/cdnjs/ajax/libs/mathjax/2.6.1/MathJax.js?config=TeX-AMS-MML_HTMLorMML
    md_extensions: +raw_html +markdown_in_html_blocks +tex_math_dollars +fancy_lists +startnum +lists_without_preceding_blankline
    self_contained: no
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
---
<script language="JavaScript">
$(function() {
  /* Lets the user click on the images to view them in full resolution. */
  $("div.figure img").wrap(function() {
    var link = $('<a/>');
    link.attr('href', $(this).attr('src'));
    link.attr('title', $(this).attr('alt'));
    link.attr('target', '_blank');
    return link;
  });
});
</script>
<p>{ <a href="https://github.com/wikimedia-research/Discovery-Search-2ndTest-BM25_jazhth/blob/master/docs/index.Rmd">RMarkdown Source</a> | <a href="https://github.com/wikimedia-research/Discovery-Search-2ndTest-BM25_jazhth">Analysis Codebase</a> }</p>
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
options(digits = 3, scipen = 500)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
path <- function(x) {
  if (grepl("docs", getwd(), fixed = TRUE)) {
    return(file.path("..", x))
  } else {
    return(x)
  }
}
# Font to go together with HTML version of report: http://www.latofonts.com/
# extrafont::font_import("~/Downloads/Lato2OFL")
```
```{r captions, echo = FALSE}
# Manual figure & table captioning:
library(magrittr)
library(captioner) # install.packages("captioner")
table_caps <- captioner(prefix = "Table")
figure_caps <- captioner(prefix = "Figure")
code_caps <- captioner(prefix = "Snippet")
# Custom caption formatting and printing:
format_caption <- function(caps, name) {
  return({
    sub(caps(name, display = "cite"),
      paste0("**", caps(name, display = "cite"),"**"),
      caps(name, display = "full"), fixed = TRUE) %>%
    sub("  ", " ", ., fixed = TRUE)
  })
}
print_caption <- function(formatted_caption) {
  cat(paste0('<p class = "caption">', formatted_caption, '</p>', collapse = ''))
}
# Add captions:
#code_caps(name = "bm25_query", caption = "Query used to extract BM25 test data from our event logging database.", display = FALSE)
#table_caps(name = "clustering_example", caption = "Example of how choice of linkage affects clustering of queries from a real search session.", display = FALSE)
table_caps(name = "group_counts", caption = "Counts of sessions anonymously tracked and events collected during the second A/B test (Oct 27 - Nov 15).", display = FALSE)
table_caps(name = "group_counts2", caption = "After searchResultPage De-duplication, Counts of sessions anonymously tracked and events collected during the second A/B test (Oct 27 - Nov 15).", display = FALSE)
#figure_caps("query_reform_counts", "Proportions of searches with 0, 1, 2, and 3+ query reformulations.", display = FALSE)
#figure_caps("query_reform_prop", "Proportions of searches where user reformulated their query.", display = FALSE)
figure_caps("zrr", "Zero results rate is the proportion of searches in which the user received zero results.", display = FALSE)
figure_caps("paulscore", "Average per-group PaulScore for various values of F (0.1, 0.5, and 0.9) with bootstrapped confidence intervals.", display = FALSE)
figure_caps("engagement_overall", "Clickthrough rates of test groups.", display = FALSE)
#figure_caps("engagement", "Clickthrough rates of test groups after splitting searches into those having query reformulations and those without query reformulations.", display = FALSE)
figure_caps("first_clicked", "First clicked result's position by group.", display = FALSE)
```

```{r install_packages, eval = FALSE}
# Install packages used in the report:
install.packages(c("devtools", "tidyverse", "binom"))
devtools::install_github("hadley/ggplot2")
# ^ development version of ggplot2 includes subtitles
devtools::install_github("wikimedia/wikimedia-discovery-polloi")
# ^ for converting 100000 into 100K via polloi::compress()
```
```{r load_packages}
# Load packages that we will be using in this report:
library(tidyverse) # for ggplot2, dplyr, tidyr, broom, etc.
library(binom) # for Bayesian confidence intervals of proportions
```

```{r paulscore_functions, cache = TRUE}
# PaulScore Calculation
query_score <- function(positions, F) {
   if (length(positions) == 1 || all(is.na(positions))) {
    # no clicks were made
    return(0)
   } else {
     positions <- positions[!is.na(positions)] # when operating on 'events' dataset, searchResultPage events won't have positions
  return(sum(F^positions))
   }
}
# Bootstrapping
bootstrap_mean <- function(x, m, seed = NULL) {
  if (!is.null(seed)) {
    set.seed(seed)
  }
  n <- length(x)
  return(replicate(m, mean(x[sample.int(n, n, replace = TRUE)])))
}
```

## Results

### Data

```{r data, cache = TRUE}
# Import events fetched from MySQL
load(path("data/ab-test_bm25.RData"))
events <- events[!duplicated(events$event_id),]
events <- events %>%
  group_by(date, wiki, test_group, session_id, search_id) %>%
  filter("searchResultPage" %in% action) %>%
  ungroup %>% as.data.frame() # remove search_id without SERP asscociated
events$test_group <- factor(
  events$test_group,
  levels = c("bm25:control", "bm25:inclinks_pv"),
  labels = c("Control Group (tf–idf)", "Using per-field query builder with incoming links and pageviews as QIFs"))
cirrus <- readr::read_tsv(path("data/ab-test_bm25_cirrus-results.tsv.gz"), col_types = "cccc")
cirrus <- cirrus[!duplicated(cirrus),]
events <- left_join(events, cirrus, by = c("event_id", "page_id", "cirrus_id"))
rm(cirrus)
```
The test was deployed on October 27th and ran for a week (thwiki ran longer, till Nov 15.), collecting a total of `r polloi::compress(nrow(events), 1)` events from `r polloi::compress(length(unique(events$search_id)), 1)` unique sessions. See `r table_caps("group_counts", display = "cite")` for counts broken down by wiki and test group.

```{r summary, results = "asis", dependson = "data"}
events_summary <- events %>%
  group_by(wiki, `Test group` = test_group) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Events recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Events recorded` = sum(.$`Events recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Events recorded` = prettyNum(`Events recorded`, big.mark = ","))
knitr::kable(events_summary, format = "markdown", align = c("l", "l", "r", "r"))
```
```{r summary_caption, results = "asis", echo = FALSE}
print_caption(format_caption(table_caps, "group_counts"))
```

An issue we noticed with the event logging is that when the user goes to the next page of search results or clicks the Back button after visiting a search result, a new page ID is generated for the search results page. The page ID is how we connect click events to search result page events. There is currently a Phabricator ticket ([T146337](https://phabricator.wikimedia.org/T146337)) for addressing these issues. For this analysis, we de-duplicated by connecting search engine results page (searchResultPage) events that have the exact same search query, and then connected click events together based on the searchResultPage connectivity.

```{r searchResultPage_deduplication, dependson = "data", cache = TRUE}
temp <- events %>%
  filter(action == "searchResultPage") %>%
  group_by(session_id, search_id, query) %>%
  mutate(new_page_id = min(page_id)) %>%
  ungroup %>%
  select(c(page_id, new_page_id)) %>%
  distinct
events <- left_join(events, temp, by = "page_id"); rm(temp)
events$new_page_id[is.na(events$new_page_id)] <- events$page_id[is.na(events$new_page_id)] 
temp <- events %>%
  filter(action == "searchResultPage") %>%
  arrange(new_page_id, ts) %>%
  mutate(dupe = duplicated(new_page_id, fromLast = FALSE)) %>%
  select(c(event_id, dupe))
events <- left_join(events, temp, by = "event_id"); rm(temp)
events$dupe[events$action != "searchResultPage"] <- FALSE
events <- events[!events$dupe & !is.na(events$new_page_id), ] %>%
  select(-c(page_id, dupe)) %>%
  rename(page_id = new_page_id) %>%
  arrange(date, session_id, search_id, page_id, desc(action), ts)
```
```{r aggregation, dependson = c("searchResultPage_deduplication", "paulscore_functions"), cache = TRUE}
# Summarize on a page-by-page basis for each SERP:
searches <- events %>%
  group_by(wiki, `test group` = test_group, session_id, search_id, page_id) %>%
  filter("searchResultPage" %in% action) %>% # filter out searches where we have clicks but not searchResultPage events
  summarize(ts = ts[1], query = query[1],
            results = ifelse(n_results_returned[1] > 0, "some", "zero"),
            clickthrough = "click" %in% action,
            `no. results clicked` = length(unique(position_clicked))-1,
            `first clicked result's position` = ifelse(clickthrough, position_clicked[2], NA),
            `result page IDs` = result_pids[1],
            `Query score (F=0.1)` = query_score(position_clicked, 0.1),
            `Query score (F=0.5)` = query_score(position_clicked, 0.5),
            `Query score (F=0.9)` = query_score(position_clicked, 0.9)) %>%
  arrange(ts)
```
After de-duplicating, we collapsed `r polloi::compress(nrow(events), 1)` (searchResultPage and click) events into `r polloi::compress(nrow(searches), 1)` searches. See `r table_caps("group_counts2", display = "cite")` for counts broken down by wiki and test group.

```{r summary2, results = "asis", dependson = c("searchResultPage_deduplication","aggregation")}
events_summary2 <- events %>%
  group_by(wiki, `Test group` = test_group) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Events recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Events recorded` = sum(.$`Events recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Events recorded` = prettyNum(`Events recorded`, big.mark = ","))
searches_summary <- searches %>%
  group_by(wiki, `Test group` = `test group`) %>%
  summarize(`Search sessions` = length(unique(search_id)), `Searches recorded` = n()) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Search sessions` = sum(.$`Search sessions`),
      `Searches recorded` = sum(.$`Searches recorded`)
    ))
  } %>%
  mutate(`Search sessions` = prettyNum(`Search sessions`, big.mark = ","),
         `Searches recorded` = prettyNum(`Searches recorded`, big.mark = ","))
knitr::kable(inner_join(searches_summary, events_summary2, by=c("wiki", "Test group", "Search sessions")), 
             format = "markdown", align = c("l", "l", "r", "r", "r"))
```
```{r summary_caption2, results = "asis", echo = FALSE}
print_caption(format_caption(table_caps, "group_counts2"))
```

There are `r polloi::compress(length(unique(events$page_id[events$action=="visitPage"])), 1)` visitPage events. See the table below for counts broken down by wiki and test group.

```{r aggregation_visits, dependson = "searchResultPage_deduplication", cache = TRUE}
# Summarize on a page-by-page basis for each visitPage:
clickedResults <- events %>%
  group_by(wiki, `test group` = test_group, session_id, search_id, page_id) %>%
  filter("visitPage" %in% action) %>% #only checkin and visitPage action
  summarize(ts = ts[1], 
            dwell_time=ifelse("checkin"%in% action, max(checkin, na.rm=T), 0),
            scroll=sum(scroll)>0) %>%
  arrange(ts)
clickedResults$dwell_time[is.na(clickedResults$dwell_time)] <- 0
```
```{r summary3, results = "asis", dependson = "aggregation_visits"}
clickedResults_summary <- clickedResults %>%
  group_by(wiki, `Test group` = `test group`) %>%
  summarize(`Visited pages` = length(unique(page_id))) %>% ungroup %>%
  {
    rbind(., tibble(
      `wiki` = "All Wikis",
      `Test group` = "Total",
      `Visited pages` = sum(.$`Visited pages`)
    ))
  } %>%
  mutate(`Visited pages` = prettyNum(`Visited pages`, big.mark = ","))
knitr::kable(clickedResults_summary, format = "markdown", align = c("l", "l", "r", "r"))
```

### Zero Results Rate

In `r figure_caps("zrr", display = "cite")`, we see that the test group had a significantly lower ZRR.

```{r zrr, dependson = "query_clustering", cache = TRUE}
zrr_pages <- searches %>%
  group_by(`test group`, results) %>%
  tally %>%
  spread(results, n) %>%
  mutate(`zero results rate` = zero/(some + zero)) %>%
  ungroup
zrr_pages <- cbind(zrr_pages, as.data.frame(binom:::binom.bayes(zrr_pages$zero, n = zrr_pages$some + zrr_pages$zero)[, c("mean", "lower", "upper")]))
```
```{r zrr_caption, echo = FALSE}
zrr_cap <- format_caption(figure_caps, "zrr")
```
```{r zrr_eda, fig.cap = zrr_cap, dependson = "zrr"}
zrr_pages %>%
  ggplot(aes(x = `test group`, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(limits = rev(levels(events$test_group))) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_color_brewer("Test Group", palette = "Set1", guide = FALSE) +
  labs(x = NULL, y = "Zero Results Rate",
       title = "Proportion of searches that did not yield any results, by test group",
       subtitle = "With 95% credible intervals.") +
  geom_text(aes(label = sprintf("%.2f%%", 100 * `zero results rate`),
                vjust = "bottom", hjust = "center"), nudge_x = 0.1) #+
  #theme_minimal(base_family = "Lato")
```
```{r zrr_eda2}
zrr_pages <- searches %>%
  group_by(wiki, `test group`, results) %>%
  tally %>%
  spread(results, n) %>%
  mutate(`zero results rate` = zero/(some + zero)) %>%
  ungroup
zrr_pages <- cbind(zrr_pages, as.data.frame(binom:::binom.bayes(zrr_pages$zero, n = zrr_pages$some + zrr_pages$zero)[, c("mean", "lower", "upper")]))
zrr_pages %>%
  ggplot(aes(x = `test group`, y = `mean`, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(limits = rev(levels(events$test_group))) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_color_brewer("Test Group", palette = "Set1", guide = FALSE) +
  labs(x = NULL, y = "Zero Results Rate",
       title = "Proportion of searches that did not yield any results, by test group and wiki",
       subtitle = "With 95% credible intervals.") +
  geom_text(aes(label = sprintf("%.2f%%", 100 * `zero results rate`),
                vjust = "bottom", hjust = "center"), nudge_x = 0.1) +
  facet_wrap(~ wiki, ncol = 3) 
```

### PaulScore

In `r figure_caps("paulscore", display = "cite")`, we see that the test group had slightly lower PaulScores.

```{r paulscores, dependson = "query_clustering", cache = TRUE}
set.seed(777)
paulscores <- searches %>%
  ungroup %>%
  filter(clickthrough==TRUE) %>% #???
  select(c(`test group`, `Query score (F=0.1)`, `Query score (F=0.5)`, `Query score (F=0.9)`)) %>%
  gather(`F value`, `Query score`, -`test group`) %>%
  mutate(`F value` = sub("^Query score \\(F=(0\\.[159])\\)$", "F = \\1", `F value`)) %>%
  group_by(`test group`, `F value`) %>%
  summarize(
    PaulScore = mean(`Query score`),
    Interval = paste0(quantile(bootstrap_mean(`Query score`, 1000), c(0.025, 0.975)), collapse = ",")
  ) %>%
  extract(Interval, into = c("Lower", "Upper"), regex = "(.*),(.*)", convert = TRUE)
```

```{r paulscores_caption, echo = FALSE}
paulscore_cap <- format_caption(figure_caps, "paulscore")
```
```{r paulscores_eda, fig.cap = paulscore_cap, dependson = "paulscores"}
paulscores %>%
  ggplot(aes(x = `F value`, y = PaulScore, color = `test group`)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), position = position_dodge(width = 0.7)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  #scale_y_continuous(limits = c(0.2, 0.35)) +
  labs(x = NULL, y = "PaulScore(F)",
       title = "PaulScore(F) by test group and value of F",
       subtitle = "With bootstrapped 95% confidence intervals.") +
  geom_text(aes(label = sprintf("%.3f", PaulScore), y = Upper + 0.01, vjust = "bottom"),
            position = position_dodge(width = 0.7)) +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom") 
```
```{r paulscores_eda2}
set.seed(777)
paulscores <- searches %>%
  ungroup %>%
  filter(clickthrough==TRUE) %>% 
  select(c(wiki, `test group`, `Query score (F=0.1)`, `Query score (F=0.5)`, `Query score (F=0.9)`)) %>%
  gather(`F value`, `Query score`, -c(`test group`, wiki)) %>%
  mutate(`F value` = sub("^Query score \\(F=(0\\.[159])\\)$", "F = \\1", `F value`)) %>%
  group_by(wiki, `test group`, `F value`) %>%
  summarize(
    PaulScore = mean(`Query score`),
    Interval = paste0(quantile(bootstrap_mean(`Query score`, 1000), c(0.025, 0.975)), collapse = ",")
  ) %>%
  extract(Interval, into = c("Lower", "Upper"), regex = "(.*),(.*)", convert = TRUE)
paulscores %>%
  ggplot(aes(x = `F value`, y = PaulScore, color = `test group`)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), position = position_dodge(width = 0.7)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  #scale_y_continuous(limits = c(0.2, 0.35)) +
  labs(x = NULL, y = "PaulScore(F)",
       title = "PaulScore(F) by wiki, test group and value of F",
       subtitle = "With bootstrapped 95% confidence intervals.") +
  geom_text(aes(label = sprintf("%.3f", PaulScore), y = Upper + 0.01, vjust = "bottom"),
            position = position_dodge(width = 0.7)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom") 
```

### Engagement

In Figures `r figure_caps("engagement_overall", display = "num")`, we see that the test group had a significantly lower Clickthrough rate.

```{r engagement_overall, dependson = "query_reformulations", cache = TRUE}
engagement_overall <- searches %>%
  filter(results=="some") %>% #???
  group_by(`test group`) %>%
  summarize(clickthroughs = sum(clickthrough > 0),
            searches = n(), ctr = clickthroughs/searches) %>%
  ungroup
engagement_overall <- cbind(
  engagement_overall,
  as.data.frame(
    binom:::binom.bayes(
      engagement_overall$clickthroughs,
      n = engagement_overall$searches)[, c("mean", "lower", "upper")]
  )
)
```
```{r engagement_overall_caption, echo = FALSE}
engagement_overall_cap <- format_caption(figure_caps, "engagement_overall")
```
```{r engagement_overall_eda, fig.cap = engagement_overall_cap, dependson = "engagement_overall"}
engagement_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Clickthrough rate",
       title = "Engagement with search results by test group") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * ctr), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom")
```
```{r engagement_overall_eda2}
engagement_overall <- searches %>%
  filter(results=="some") %>% 
  group_by(wiki, `test group`) %>%
  summarize(clickthroughs = sum(clickthrough > 0),
            searches = n(), ctr = clickthroughs/searches) %>%
  ungroup
engagement_overall <- cbind(
  engagement_overall,
  as.data.frame(
    binom:::binom.bayes(
      engagement_overall$clickthroughs,
      n = engagement_overall$searches)[, c("mean", "lower", "upper")]
  )
)
engagement_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Clickthrough rate",
       title = "Engagement with search results by test group and wiki") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * ctr), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom")
```

### First Clicked Result's Position

In `r figure_caps("first_clicked", display = "cite")`, we see that test group users were less likely to click on the first search result first than the control group.

```{r first_clicked_position, dependson = "query_reformulations", cache = TRUE}
safe_ordinals <- function(x) {
  return(vapply(x, toOrdinal::toOrdinal, ""))
}
first_clicked <- searches %>%
  filter(results == "some" & clickthrough & !is.na(`first clicked result's position`)) %>%
  mutate(`first clicked result's position` = ifelse(`first clicked result's position` < 4, safe_ordinals(`first clicked result's position` + 1), "5th or higher")) %>%
  group_by(`test group`, `first clicked result's position`) %>%
  tally %>%
  mutate(total = sum(n), prop = n/total) %>%
  ungroup
set.seed(0)
temp <- as.data.frame(binom:::binom.bayes(first_clicked$n, n = first_clicked$total, tol = .Machine$double.eps^0.1)[, c("mean", "lower", "upper")])
first_clicked <- cbind(first_clicked, temp); rm(temp)
```
```{r first_clicked_position_caption, echo = FALSE}
first_clicked_cap <- format_caption(figure_caps, "first_clicked")
```
```{r first_clicked_position_eda, fig.cap = first_clicked_cap, dependson = "first_clicked_position"}
first_clicked %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  geom_text(aes(label = sprintf("%.1f", 100 * prop), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0.005), breaks = seq(0, 1, 0.01)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  facet_wrap(~ `first clicked result's position`, scale = "free_y", nrow = 1) +
  labs(x = NULL, y = "Proportion of searches",
       title = "Position of the first clicked result",
       subtitle = "With 95% credible intervals") +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "gray90"),
        panel.border = element_rect(color = "gray30", fill = NA))
```
```{r first_clicked_position_eda2, fig.height=10 }
first_clicked <- searches %>%
  filter(results == "some" & clickthrough & !is.na(`first clicked result's position`)) %>%
  mutate(`first clicked result's position` = ifelse(`first clicked result's position` < 4, safe_ordinals(`first clicked result's position` + 1), "5th or higher")) %>%
  group_by(wiki, `test group`, `first clicked result's position`) %>%
  tally %>%
  mutate(total = sum(n), prop = n/total) %>%
  ungroup
set.seed(0)
temp <- as.data.frame(binom:::binom.bayes(first_clicked$n, n = first_clicked$total, tol = .Machine$double.eps^0.1)[, c("mean", "lower", "upper")])
first_clicked <- cbind(first_clicked, temp); rm(temp)
first_clicked %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  geom_text(aes(label = sprintf("%.1f", 100 * prop), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent_format(),
                     expand = c(0, 0.005), breaks = seq(0, 1, 0.01)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  facet_wrap(~ wiki+`first clicked result's position`, scale = "free_y", ncol=5, nrow = 3) +
  labs(x = NULL, y = "Proportion of searches",
       title = "Position of the first clicked result",
       subtitle = "With 95% credible intervals") +
  #theme_minimal(base_family = "Lato") +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "gray90"),
        panel.border = element_rect(color = "gray30", fill = NA))
```

### Dwell Time per visit page

The figures below show the survival curve for each test group and wikis. Except zhwiki, users are more likely to stay longer on visit pages.

```{r dwell_time_eda}
clickedResults %>%
  split(.$`test group`) %>% 
  map_df(function(df) {
    seconds <- c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420)
    seshs <- as.data.frame(do.call(cbind, lapply(seconds, function(second) {
      return(sum(df$dwell_time >= second))
    })))
    names(seshs) <- seconds
    return(cbind(`test group` = head(df$`test group`, 1), n = seshs$`0`, seshs, `450`=seshs$`420`))
  }) %>%
  gather(seconds, visits, -c(`test group`, n)) %>%
  mutate(seconds = as.numeric(seconds)) %>%
  group_by(`test group`, seconds) %>%
  mutate(proportion = visits/n) %>%
  ungroup() %>%
  ggplot(aes(group=`test group`, color=`test group`)) +
  geom_step(aes(x = seconds, y = proportion), direction = "hv") +
  scale_x_continuous(name = "T (Dwell Time)", breaks=c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420))+ 
  scale_y_continuous("Proportion of visits longer than T", labels = scales::percent_format(),
                     breaks = seq(0, 1, 0.1)) +
  theme(legend.position = "bottom")
```

```{r dwell_time_eda_wiki}
clickedResults %>%
  split(list(.$wiki, .$`test group`)) %>% 
  map_df(function(df) {
    seconds <- c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420)
    seshs <- as.data.frame(do.call(cbind, lapply(seconds, function(second) {
      return(sum(df$dwell_time >= second))
    })))
    names(seshs) <- seconds
    return(cbind(wiki=head(df$wiki, 1), `test group` = head(df$`test group`, 1), n = seshs$`0`, seshs, `450`=seshs$`420`))
  }) %>%
  gather(seconds, visits, -c(wiki, `test group`, n)) %>%
  mutate(seconds = as.numeric(seconds)) %>%
  group_by(wiki, `test group`, seconds) %>%
  mutate(proportion = visits/n) %>%
  ungroup() %>%
  ggplot(aes(group=`test group`, color=`test group`)) +
  geom_step(aes(x = seconds, y = proportion), direction = "hv") +
  scale_x_continuous(name = "T (Dwell Time)", breaks=c(0, 10, 20, 30, 40, 50, 60, 90, 120, 150, 180, 210, 240, 300, 360, 420))+ 
  scale_y_continuous("Proportion of visits longer than T", labels = scales::percent_format(),
                     breaks = seq(0, 1, 0.1)) +
  theme(legend.position = "bottom") +
  facet_wrap(~ wiki, ncol=1, nrow =3)
```

### Proportion of visit pages with scroll

Users in the test group are more likely to scroll on the visit page, but the differences are not statistically significant.

```{r scroll_eda}
scroll_overall <- clickedResults %>%
  group_by(`test group`) %>%
  summarize(scrolls=sum(scroll), visits=n(), proportion = sum(scroll)/n()) %>%
  ungroup
scroll_overall <- cbind(
  scroll_overall,
  as.data.frame(
    binom:::binom.bayes(
      scroll_overall$scrolls,
      n = scroll_overall$visits)[, c("mean", "lower", "upper")]
  )
)
scroll_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Proportion of visits",
       title = "Proportion of visits with scroll by test group") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  theme(legend.position = "bottom")
```

```{r scroll_eda_wiki}
scroll_overall <- clickedResults %>%
  group_by(wiki, `test group`) %>%
  summarize(scrolls=sum(scroll), visits=n(), proportion = sum(scroll)/n()) %>%
  ungroup
scroll_overall <- cbind(
  scroll_overall,
  as.data.frame(
    binom:::binom.bayes(
      scroll_overall$scrolls,
      n = scroll_overall$visits)[, c("mean", "lower", "upper")]
  )
)
scroll_overall %>%
  ggplot(aes(x = 1, y = mean, color = `test group`)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(width = 1)) +
  scale_color_brewer("Test Group", palette = "Set1", guide = guide_legend(ncol = 2)) +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.01, 0.01)) +
  labs(x = NULL, y = "Proportion of visits",
       title = "Proportion of visits with scroll by test group and wiki") +
  geom_text(aes(label = sprintf("%.1f%%", 100 * proportion), y = upper + 0.0025, vjust = "bottom"),
            position = position_dodge(width = 1)) +
  facet_wrap(~ wiki, ncol = 3) +
  theme(legend.position = "bottom")
```